Learning constraints in tabular data

### 2016-05-11 Paper/ECAI/tabular.tex
some tweaks to problem statement

\paragraph{Example}
A first example is $permutation(G') \rightarrow alldifferent(G')$ (it can be seen in Table~\ref{table:constraints} that both constraints only hold if $G'$ is a vector). In this case the arguments are the same in both constraints. For most applications, it will be sufficient to output only the most specific one.
A more involved example is that a look-up constraint implies a foreign-key constraint. The syntax of the look-up constraint is $\eclookup{G'_2}{G'_1}{H'_1}{H'_2}$, where the values in the vector $G'_2$ are determined by looking up the corresponding value in vector $G'_1$ in vector $H'_1$ and returning the corresponding value in vector $H'_2$. In Figure~\ref{fig:main_example} we have $\eclookup{\range{T_{4}}{\rangeall}{3}}{\range{T_{4}}{\rangeall}{2}}{\range{T_{1}}{\rangeall}{1}}{\range{T_{1}}{\rangeall}{2}}$. This implies a foreign-key constraint $\ecfkey{G'_1}{H'_1}$ where each of the values in vector $G'_1$ must appear in $H'_1$ for the look-up to work.

Two constraints are \textit{equivalent} if they imply each other. More formally, $\forall G'_1, ..., G'_n$ s.t. $\{G''_1, ..., G''_n\} = \{G'_1, ..., G'_n\},\, c_1(G'_1, ... G'_n) \leftrightarrow c_2(G''_1, ..., G''_n)$.
An example within the same \template is for the sum over vectors constraint: $G_1 = +(G_2, G_3) \leftrightarrow G_1 = +(G_3, G_2)$. A related example over multiple constraints is $G_1 = +(G_2, G_3) \leftrightarrow G_1 = SUM(H)$ with $size(H) = 2$ and $G_2 \subset H, G_3 \subset H$.

@@

>>>>

\paragraph{Example}
A first example is $permutation(G') \rightarrow alldifferent(G')$ (it can be seen in Table~\ref{table:constraints} that both constraints only hold if $G'$ is a vector). In this case the arguments are the same in both constraints. For most applications, it will be sufficient to output only the most specific one.
A more involved example is that a look-up constraint implies a foreign-key constraint. The syntax of the look-up constraint is $\eclookup{G'_2}{G'_1}{H'_1}{H'_2}$, where the values in the vector $G'_2$ are determined by looking up the corresponding value of vector $G'_1$ in vector $H'_1$ and returning the corresponding value in vector $H'_2$. In Figure~\ref{fig:main_example} we have $\eclookup{\range{T_{4}}{\rangeall}{3}}{\range{T_{4}}{\rangeall}{2}}{\range{T_{1}}{\rangeall}{1}}{\range{T_{1}}{\rangeall}{2}}$. This implies a foreign-key constraint $\ecfkey{G'_1}{H'_1}$ where each of the values in vector $G'_1$ must appear in $H'_1$ for the look-up to work.

Another form of redundancy is because of \textit{equivalent} constraints.
Two constraints are equivalent if they imply each other. More formally, $\forall G'_1, ..., G'_n$ s.t. $\{G''_1, ..., G''_n\} = \{G'_1, ..., G'_n\},\, c_1(G'_1, ... G'_n)$ $\leftrightarrow c_2(G''_1, ..., G''_n)$.
An example within the same \template is for the sum over vectors constraint: $G_1 = +(G_2, G_3) \leftrightarrow G_1 = +(G_3, G_2)$. A related example over multiple constraints is $G_1 = +(G_2, G_3) \leftrightarrow G_1 = SUM(H)$ with $size(H) = 2$ and $G_2 \subset H, G_3 \subset H$.

@@

Because dealing with redundancy is often application-dependent, we explain in the next section our generic method for finding all constraints.
